Fixed-Shape Ellipse by Three Points

### 2019-10-18 ONPCE/slides.tex
wip

	\begin{itemize}
		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
	\end{itemize}
\end{frame}

@@

>>>>

	\begin{itemize}
		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
		\item This can be done in $\bigO(n^2)$.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Chebyshev Interpolation}
	Choosing the degree of the interpolation:

	\begin{itemize}
		\item There is no guaranteed way to choose it.
		\item A good rule is to examine the last coefficient.
		\item For a predefined $\epsilon$, choose $n$, such that:

		\begin{equation*}
		|a_n| \le \epsilon
		\end{equation*}

		\item There are other ways like checking the error on a Lobatto grid.
	\end{itemize}
\end{frame}

\begin{frame}{Chebyshev Interpolation}
	For $n=32$, a precision of $10^{-10}$ is expected.

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{error_coef}
		\caption{$|a_n|$ for the interpolation of $\xi$ for an instance.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Chebyshev Interpolation}{Roots}
	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix. This is it for $n=5$:

	\begin{equation*}
	\left[\begin{array}{cccccc}
	0&1&0&0&0\\
	\frac{1}{2} & 0 & \frac{1}{2} & 0 & 0\\
	0 & \frac{1}{2} & 0 & \frac{1}{2} & 0\\
	0 & 0 & \frac{1}{2} & 0 & \frac{1}{2}\\
	-\frac{a_0}{2a_5} & -\frac{a_1}{2a_5} &-\frac{a_2}{2a_5} &-\frac{a_3}{2a_5} &-\frac{a_4}{2a_5}\\
	\end{array}\right]
	\end{equation*}

	\begin{itemize}
		\item This matrix is a Hessenberg matrix.
		\item Its eigenvalues can be found by a QR algorithm in $\bigO(n^3)$.
	\end{itemize}
\end{frame}

\begin{frame}{Chebyshev Interpolation}{Roots}
	The largest error on roots that were found for $n=32$ is around $10^{-14}$ for an instance:
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{error_roots}
		\caption{$|\xi(\hat{\theta})|$, where $\hat{\theta}$ is a root of $f_n$.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Chebyshev Interpolation}{Roots}
	The experiments were made using Python with the NumPy library. The running time is really low, even for $n=64$.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{running_time}
		\caption{The running time to find the roots of $f_n$.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Example}
	An example with $4$ solutions.\cite{andreta}.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{e3psol012}
		\caption{An example with $4$ solutions.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}
